Manuscript Preparation

### 2018-06-29 Houston/src/manuscript_preparation.Rmd
Minor change to manuscript_prep.Rmd

compareTable <- table (labeled.data.lost.train$severe, predict(svm.model))  # tabulate
mean(labeled.data.lost.train$severe != predict(svm)) # misclassification rate

>>>>

compareTable <- table (labeled.data.lost.train$severe, predict(svm.model))  # tabulate
mean(labeled.data.lost.train$severe != predict(svm.model)) # misclassification rate
